### 2021-02-01 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
将 globally 翻译成中文

\chapter{GLOBALLY SPATIAL-TEMPORAL PERCEPTION: A LONG-TERM TRACKING SYSTEM}\label{chap:globally}

\section{Abstract}
Although siamese trackers have achieved superior performance, these kinds of approaches tend to favour the local search mechanism and are thus prone to accumulating inaccuracies of predicted positions, leading to tracking drift over time, especially in long-term tracking scenario. To solve these problems, we propose a siamese tracker in the spirit of the faster RCNN's two-stage detection paradigm. This new tracker is dedicated to reducing cumulative inaccuracies and improving robustness based on a global perception mechanism, which allows the target to be retrieved in time spatially over the whole image plane. Since the very deep network can be enabled for feature learning in this two-stage tracking framework, the power of discrimination is guaranteed. What's more, we also add a CNN-based trajectory prediction module exploiting the target's temporal motion information to mitigate the interference of distractors.
These two spatial and temporal modules exploit both the high-level appearance information and complementary trajectory information to improve the tracking robustness. Comprehensive experiments demonstrate that the proposed Globally Spatial-Temporal Perception-based tracking system performs favorably against state-of-the-art trackers.

\section{Introduction}
\label{sec:intro}

Object tracking \cite{Leang2018OnlineFO, Wang2019VisualOT, Zhang2018UsingFL} is a challenging problem in the field of computer vision, which aims to establish the positional relationship of the object to be tracked in a continuous video sequence.
The popular siamese trackers \cite{bertinetto2016fully, li2018high, Wang2018SiamMask} are typically based on the local search mechanism: \HL{searching the target} within a small neighborhood centered on the target position of the previous frame to determine \HL{its current position}.
This mechanism works \HL{well if} the target only has a small displacement between two adjacent frames.
\HL{It also brings benefits in another aspect, which is} to avoid interference from the distractors in the background.

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/globally/visulization.pdf}
    \caption{A comparison of our method with the stage-of-the-art trackers SiamMask \cite{Wang2018SiamMask} and SiamFCv2 \cite{bertinetto2016fully} in challenging situations. The example frames are from the GOT-10k \cite{huang2018got} testing set.
    % Our approach performs better compared to existing approaches.
    }
    \label{fig:visulization}
\end{figure}

However, the local search mechanism \HL{bears} some shortcomings.
First, \HL{it could cause irreversible cumulative errors if the predictions of the target positions in the previous frames drift away due to challenging illumination change, motion blur, \textit{etc.}, because the search area generated in the current frame may not cover the target leading to a complete failure in subsequent frames.}
\HL{Second, it is difficult for the local mechanism-based trackers} to meet the needs of long-term tracking \cite{kalal2011tracking, hong2015multi}.
Under the long-term \HL{scenario, the target frequently re-enters and re-exits} the screen.
\HL{Since the tracker cannot set the correct search area when the target leaves and re-enters the screen, it often fails to retrieve the target due to the wrong search area without the target covered.}

Inspired by faster RCNN's two stage detection paradigm \cite{ren2015faster}, we propose a \HL{siamese} tracker based on the global perception mechanism.
During the tracking process, \HL{our tracker} is always able to perceive the target \HL{over} the entire image.
Therefore, even if the tracker makes a mistake due to \HL{the challenging target appearance variations, the target can still be retrieved in time once its appearance returns to normal. Especially under the long-term out-of-view disappearance scenario, where the tracker cannot find the target in the full image when the target leaves the screen, our tracker can continue to work when the target re-enters the screen from any position.}

\HL{Besides the above globally spatial perception mechanism, we also propose a temporal motion model to mitigate the interference of distractors. It is known that the siamese-based tracking framework is sometimes plagued by distractors because it is difficult for the end-to-end trained siamese matching network to distinguish well between objects that look very similar. Different from the simply designed hand-crafted strategies \cite{bertinetto2016fully, li2018high}, our proposed CNN-based motion model is end-to-end trained and can predict the target current position distribution using its historical trajectory information and current target appearance information.}
\HL{Specifically,} the motion \HL{patterns} are automatically learned from the trajectory dataset \HL{in the training phase instead of} the hand-crafted features or rules \cite{iswanto2017visual}\HL{; in the testing phase,} we can use the position information of any number of historical frames instead of just the previous frame for prediction.

\iffalse
Another advantage of this globally spatial-temporal perception mechanism is that it use the RoI Align \cite{He2018MaskR} operation to enable the tracker to take advantage of deeper networks \HL{for feature learning, which is not acceptable for the popular local mechanism-based SiamFC \cite{bertinetto2016fully} and SiamRPN \cite{li2018high} trackers, because the padding in their network structures} will destroy the strict translation invariance \cite{bertinetto2016fully}. \HL{Specifically}, the entire template image and search image in our tracker are sent to the same backbone network to extract features,  \HL{and} then the object features are obtained \HL{using} the RoI Align operation from the template features according to the ground truth of the \HL{initial frame}. The object features and the search \HL{image} features are cross-correlated by channel to obtain \HL{a fusion feature map}, which \HL{is} sent to the subsequent tracking \HL{modules}. \HL{Since this new} solution has no restrictions on the \HL{translation invariance, we} can use the powerful ResNet \cite{he2016deep} as the backbone network \HL{to accurately model the discrimination between the foreground object and background clutters.}
\fi

\iffalse
To sum up, this paper makes following three main contributions.
(1) Based on the global perception mechanism, we introduce a two stage tracking pipeline using a very deep network to reduce cumulative inaccuracies and improve robustness.
(2) A novel unified end-to-end convolutional neural network architecture \HL{for} trajectory prediction is proposed, where historical trajectory information and appearance information of the current frame are used to predict the target position distribution.
(3) We demonstrate the effectiveness of our proposed 
Globally Spatial-Temporal Perception-based tracking system (GSTP)
\HL{by showing} that the tracking performance \HL{performs favorably against}
other state-of-the-art approaches on the \HL{GOT-10k \cite{huang2018got} and UAV20L \cite{mueller2016benchmark} Long-term Tracking datasets}.
\fi

\section{THE PROPOSED ALGORITHM}
\label{sec:method}

\iffalse
\begin{figure}[t]
    \includegraphics{images/Arch7.pdf}
    \caption{Architecture of our Globally Spatial-Temporal Perception-based (GSTP) tracking system.}
    \label{fig:arch}
\end{figure}
\fi

@@

Our method explores the key idea that the task of visual object tracking can be tackled by splitting it into first extracting candidate targets, followed by eliminating distractors using the motion model.
By adopting this paradigm, we can achieve better performance by designing a more accurate tracking component and a more robust motion model, especially in the long-term scenario.

%To solve the cumulative error caused by local search, 
Specifically, we propose the Globally Spatial-Temporal Perception tracking system, which means: (1) We use an entire image instead of a small image patch as the input to the tracker to provide the global spatial information for it.  (2) In order to better perceive the global spatial information, we propose a two-stage tracking component, which is able to detect candidate targets that are visually similar to the ground truth target. (3) To perceive the temporal information, we propose a motion model, which is able to exclude the distractors by predicting the location distribution to obtain the final tracking result.

@@

\subsection{Tracking component}

We build our tracking component based on the popular object detection architecture --- faster RCNN \cite{ren2015faster}. Although the use of object detection modules and siamese-based feature extractor for object tracking is not first proposed in this paper, our tracker has advantages over relevant tracking algorithms \cite{li2018high, Wang2018SiamMask, danelljan2019atom, voigtlaender2019siam}. Compared with SiamRPN \cite{li2018high}, whose input is always image patches with target located at the center, the input of our tracking component is the entire image, which means the target may appear at any spatial location. This prevents the network from learning bias to the center location, thereby breaking the spatial invariance restriction \cite{li2019siamrpn++} of the network architecture. As a result, the very deep networks such as ResNet50 \cite{he2016deep} can be used as the feature extractor of the tracking component. For detailed explain about spatial invariance restriction and center bias, please refer to \cite{li2019siamrpn++}.
%because the input of the network is the entire image, instead of the image patch centered on the target, the target will appear in any poisition in the image, so we do not need the network has strict spatial invariance restriction \cite{li2019siamrpn++}, so we can use a deeper feature extractor, i.e., resnet50. 
Compared with SiamRPN \cite{li2018high} and SiamMask \cite{Wang2018SiamMask}, we use a two stage architecture. The second stage (RoI head \cite{ren2015faster}) can distinguish the foreground and background more effectively.
Compared with SiamMask \cite{Wang2018SiamMask} and ATOM \cite{danelljan2019atom}, our tracker can search for the target in the whole image, which allows the target to be retrieved in time spatially after the tracking module makes a mistake.
Compared with Siam R-CNN \cite{voigtlaender2019siam}, whose backbone and RPN are frozen, our tracker generate the target-specific features before RPN, and the whole network can be trained end to end. In object tracking, a target may be foreground in one video and background in another. Therefore, the candidates generated by our RPN can better meet the requirements of general object tracking.
%(The backbone and RPN are frozen and only the redetection head (after concatenation) is trained for tracking) they fixed the parameters in the backbone and the RPN. Only the second stage is used for target spercific tracking, which is not good for "generatic" object tracking: because some objects are foreground in some cases and background in others. Instead, our tracker use the correlation before RPN, the "target" which is good for general object tracking. The architecture of our tracking component is described as follows:

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
To describe our tracking component, we we first briefly revisit faster RCNN. It consists of a feature extractor followed by two detection stages: the RPN head and the RoI head.
The feature extractor $\phi_{1}$ is a variant of ResNet50. The first stage uses a region proposal network (RPN) to slide on the last feature map of the backbone layers and predict whether there is an object or not and also predict the bounding box of those objects. The second stage (\textit{i.e.}, RoI head) is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region. 
Each RoI (Region of Interest) is classified as a specific category using a classification layer and the bounding box is refined using a regression layer.
Please refer to \cite{ren2015faster} for more detailed information.

For the task of object tracking, there are two inputs to the feature extractor $\phi_{1}$: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
After generating the template feature $f_{z} = \phi_{1}(z)$ and search feature $f_{x} = \phi_{1}(x)$, we crop the object feature $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$ by the RoI Align operation \cite{He2018MaskR} from the template features according to the ground truth of the target:
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{z}),
\end{equation}
where $\mathcal{R}$ represents the RoI Align operator and $b_{obj}$ is the ground truth bounding box of the target.
Next, the search feature and the object feature are merged via the depth-wise cross-correlation \cite{li2019siamrpn++}:
\begin{equation}
    f_{corr} = f_{obj} * f_{x},
\end{equation}
where $f_{corr}$ is the fusion feature and $*$ is the depth-wise cross-correlation operator.
%The use of RPN (region proposal network) is ...
Then $f_{corr}$ is sent to the RPN head to generate candidates $B=\{b^{i}_{roi}\}^{i=1:N}$.
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
At a second stage, the RoI Align operation is performed on the fusion feature $f_{corr}$, generating a small feature map with a channel dimension of 2048 and a fixed spatial extent of 7 $\times$ 7 for every RoI:
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
where $b_{roi}^{i}$ is the bounding box of candidate region $i$.
Finally, each RoI is classified as foreground/background. During testing, we select top $K$ ranked RoI as the candidate targets, which will be post-processed in the motion model.

@@

\subsection{Motion model} After detecting object regions that are visually similar to the given first-frame template object with our tracking component, we use a motion model to eliminate distractors and obtain the final tracking result.
The motion model works in an end-to-end manner by learning the target position distribution using historical trajectory information and appearance information of the current frame.
It then rescores the candidate targets according to the position distribution, which is a 2D heatmap measuring the likelihood that the target is located at each spatial location.

Let $H_{t}^{k} = \{h_{t-i}\}_{i=1:k}$ denote the historical trajectory information, where $t$ is the index of the current frame, $k$ is the length of history, and $h_{j} = \{x_{j}, y_{j}\}$ is a two-dimensional coordinate representing the position of the target in frame $j$.
Inspired by the pose estimation task, we present $h_{j}$ as a two-dimensional heatmap $m_{j} \in \mathbb R^{h \times w}$ with a 2D Gaussian centered on the target position $(x_{j}, y_{j})$.
To model the temporal information,  The generated $k$ heatmaps are concatenated according to the time order to obtain the trajectory tensor $\mathcal{M} \in \mathbb{R}^{k \times h \times w}$ with channel dimension $k$: 
\begin{equation}
    \mathcal{M}_{t}^{k} = \mathcal{C}(m_{t-k}, m_{t-k+1}, ..., m_{t-1}),
\end{equation}
where $\mathcal{C}(\cdot)$ is the concatenation operation.

Our motion model not only utilizes the historical trajectory information for prediction, but also considers the appearance information of the current frame.
To achieve this, the RGB image of the current frame $\mathcal{I} \in \mathbb{R}^{3 \times h \times w}$ and the trajectory tensor are concatenated to obtain the enhanced trajectory tensor $\mathcal{N} \in \mathbb{R}^{(3+k) \times h \times w}$ with channel dimension $(3+k)$:
\begin{equation}
    \mathcal{N}_{t}^{k} = \mathcal{C}(\mathcal{I}_{t}, \mathcal{M}_{t}^{k}).
\end{equation}
Assuming $\phi_{2}$ is the motion model, which is a CNN network, the output of $\phi_{2}$ is calculated as follows:
\begin{equation}
    \mathcal{O}_{t}^{k} = \phi_{2}(\mathcal{N}_{t}^{k}),
\end{equation}
where $\mathcal{O}_{t}^{k} \in \mathbb{R}^{h \times w}$ is a 2D heatmap reflecting the position distribution of the target in the frame $t$.

The network of our motion model $\phi_{2}$ is the same as the pose estimation network HRNet \cite{sun2019deep}. 
\iffalse
The main reason why the pose estimation network can be used to design the motion model is that the output of the pose estimation network is the position distribution of joint points, and the output of the motion model is the position distribution of the target. This means that there is a great deal of commonality between the two tasks. In order to use HRNet for trajectory estimation, we need to change the input and output of HRNet and keep the network structure unchanged.

During tracking the $i$-th frame, we utilize the position information of the previous $K$ frames as the input to the network.
Specifically, for a historical frame, a heat map is generated by applying 2D Gaussian with stand deviation of 3 pixels centered on the target position in that frame.
The generated $K$ heatmaps are concatenated according to the time order to obtain the \textbf{trajectory tensor} with channel dimension $K$.
Our motion model not only utilizes the historical trajectory information for prediction, but also considers the appearance information of the current frame.
To achieve this, the RGB image of the current frame and the trajectory tensor are concatenated to obtain the tensor with channel dimension $(3+K)$. This tensor is sent to the network, and the output of the network is a heatmap reflecting the position distribution of the target in the current frame. The loss function, defined as the mean squared error, is applied for comparing the predicted heatmap and the groundtruth heatmap. The groundtruth heatmap is generated by applying 2D Gaussian with standard deviation of 3 pixels centered on the target position in the current frame. The network structure of our motion model is the same as HRNet. 
\fi
A brief description is provided here. The first stage of HRNet is a high-resolution subnetwork. Then high-to-low resolution subnetworks are added one by one to form more stages. The multi-resolution subnetworks are connected in parallel. Repeated multi-scale fusions are conducted by exchanging the information across the parallel multi-resolution subnetworks over and over through the whole process. We estimate the position distribution over the high resolution representations output by HRNet. Please refer to \cite{sun2019deep} for details of the network structure.

\section{EXPERIMENTS}
\label{sec:experiments}
\iffalse
\begin{figure}[htb]
    \includegraphics[width=8.6cm]{images/success_plot.png}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.
}
    \label{fig:ao}
\end{figure}
\fi

\subsection{Implementation details}
Our tracking component is trained on the GOT-10k \cite{huang2018got} training set. It contains more than 10000 video segments of real-world moving objects and over 1.5 million manually labeled bounding boxes, which covers 563 classes of real-world moving objects and 87 classes of motion patterns.
We perform multi-scale training: the target size varies from $64 \times 64$ to $256 \times 256$. The image size remains the same during the tracking progress. The tracking component is trained with stochastic gradient descent (SGD). We use a weight decay of $10^{-4}$ and momentum of 0.9. We train the tracking component for 27k iterations. The learning rate is decreased from $10^{-2}$ to $10^{-4}$.

The motion model is also trained on the GOT-10k training set. The Adam optimizer \cite{kingma2014adam} is adopted for training. The base learning rate is set as $10^{-3}$, and is dropped to $10^{-4}$ and $10^{-5}$ at the 170th and 200th epochs, respectively. The training process is terminated within 210 epochs.

>>>>

\chapter{全球时空感知：长期跟踪系统}\label{chap:globally}

\section{摘要}
尽管暹罗跟踪器已经取得了出色的性能，但是这些方法倾向于使用局部搜索机制，因此倾向于累积预测位置的不准确性，从而导致跟踪随时间的漂移，尤其是在长期跟踪情况下。为了解决这些问题，我们本着更快的RCNN的两阶段检测范例的精神，提出了一种暹罗跟踪器。这种新的跟踪器致力于基于全局感知机制来减少累积的不准确性并提高鲁棒性，该机制可在整个图像平面上及时在空间上检索目标。由于可以在此两阶段跟踪框架中启用非常深的网络进行特征学习，因此可以保证区分的能力。此外，我们还添加了基于CNN的轨迹预测模块，该模块利用目标的时间运动信息来减轻干扰因素的干扰。
这两个空间和时间模块利用高级外观信息和互补轨迹信息来提高跟踪的鲁棒性。全面的实验表明，所提出的基于全球时空知觉的跟踪系统的性能优于最先进的跟踪器。

\section{简介}
\label{sec:intro}

目标跟踪 \cite{Leang2018OnlineFO, Wang2019VisualOT, Zhang2018UsingFL} 是计算机视觉领域中一个具有挑战性的问题，该目标旨在建立连续视频序列中待跟踪目标的位置关系。
流行的暹罗跟踪器 \cite{SiamFC, SiamRPN, Wang2018SiamMask} 通常基于本地搜索机制： \HL{搜索目标} 在以前一帧的目标位置为中心的小邻域中确定 \HL{其当前位置}.
如果目标仅在两个相邻帧之间具有较小的位移，则此机制起作用。这在另一个方面也带来了好处，避免了来自干扰因素的干扰。

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/globally/visulization.pdf}
    \caption{我们的方法与最先进的跟踪器SiamMask \cite{Wang2018SiamMask} 和SiamFCv2\cite{SiamFC} 的比较。示例帧来自GOT-10k \cite{GOT-10k} 测试集中。
    % Our approach performs better compared to existing approaches.
    }
    \label{fig:visulization}
\end{figure}

但是，本地搜索机制有一些缺点。
首先，如果由于挑战性的照明变化，运动模糊等而导致先前帧中目标位置的预测偏离了预期，则可能会导致不可逆的累积误差，因为当前帧中生成的搜索区域可能会无法覆盖导致后续帧完全失败的目标。
其次，基于本地机制的跟踪器很难满足长期跟踪的需求 \cite{kalal2011tracking, hong2015multi}.
在长期情况下，目标经常重新进入并重新出现屏幕。
由于当目标离开并重新进入屏幕时跟踪器无法设置正确的搜索区域，因此由于错误的搜索区域而没有覆盖目标，跟踪器通常无法检索目标。

受更快的RCNN的两阶段检测范例 \cite{ren2015faster}的启发，我们提出了一种基于全局感知机制的孪生跟踪器。
在跟踪过程中，我们的跟踪器始终能够感知整个图像中的目标。
因此，即使跟踪器由于具有挑战性的目标外观变化而犯了一个错误，一旦目标的外观恢复正常，仍然可以及时检索目标。尤其是在长期视野外消失的情况下，当目标离开屏幕时跟踪器无法在完整图像中找到目标，而当目标从任何位置重新进入屏幕时，我们的跟踪器可以继续工作。

除了上述全局空间感知机制外，我们还提出了一种时间运动模型来减轻干扰因素的干扰。众所周知，基于暹罗的跟踪框架有时会受到干扰因素的困扰，因为端到端训练有素的暹罗匹配网络很难很好地区分看起来非常相似的对象。与简单设计的手工策略 \cite{SiamFC, SiamRPN}不同，我们提出的基于CNN的运动模型经过端到端训练，可以使用其历史轨迹信息和当前目标外观信息来预测目标当前位置分布。
具体来说，运动模式是在训练阶段从轨迹数据集自动学习的，而不是手工制作的特征或规则 \cite{iswanto2017visual}；在测试阶段，我们可以使用任意数量的历史帧的位置信息，而不仅仅是先前的帧进行预测。

\iffalse
Another advantage of this globally spatial-temporal perception mechanism is that it use the RoI Align \cite{He2018MaskR} operation to enable the tracker to take advantage of deeper networks \HL{for feature learning, which is not acceptable for the popular local mechanism-based SiamFC \cite{SiamFC} and SiamRPN \cite{SiamRPN} trackers, because the padding in their network structures} will destroy the strict translation invariance \cite{SiamFC}. \HL{Specifically}, the entire template image and search image in our tracker are sent to the same backbone network to extract features,  \HL{and} then the object features are obtained \HL{using} the RoI Align operation from the template features according to the ground truth of the \HL{initial frame}. The object features and the search \HL{image} features are cross-correlated by channel to obtain \HL{a fusion feature map}, which \HL{is} sent to the subsequent tracking \HL{modules}. \HL{Since this new} solution has no restrictions on the \HL{translation invariance, we} can use the powerful ResNet \cite{he2016deep} as the backbone network \HL{to accurately model the discrimination between the foreground object and background clutters.}
\fi

\iffalse
To sum up, this paper makes following three main contributions.
(1) Based on the global perception mechanism, we introduce a two stage tracking pipeline using a very deep network to reduce cumulative inaccuracies and improve robustness.
(2) A novel unified end-to-end convolutional neural network architecture \HL{for} trajectory prediction is proposed, where historical trajectory information and appearance information of the current frame are used to predict the target position distribution.
(3) We demonstrate the effectiveness of our proposed 
Globally Spatial-Temporal Perception-based tracking system (GSTP)
\HL{by showing} that the tracking performance \HL{performs favorably against}
other state-of-the-art approaches on the \HL{GOT-10k \cite{GOT-10k} and UAV20L \cite{mueller2016benchmark} Long-term Tracking datasets}.
\fi

\section{拟议的算法}
\label{sec:method}

\iffalse
\begin{figure}[t]
    \includegraphics{images/Arch7.pdf}
    \caption{我们基于全球时空感知（GSTP）的跟踪系统的架构。}
    \label{fig:arch}
\end{figure}
\fi

@@

我们的方法探索了一个关键思想，即将视觉对象跟踪任务分解为首先提取候选目标，然后使用运动模型消除干扰因素，从而可以解决该任务。
通过采用这种范例，我们可以通过设计更精确的跟踪组件和更健壮的运动模型来获得更好的性能，尤其是在长期情况下。

%要解决由本地搜索引起的累积错误，
具体而言，我们提出了全球时空感知跟踪系统，这意味着：（1）我们使用整个图像而不是小的图像块作为跟踪器的输入，以为其提供全局空间信息。 （2）为了更好地感知全局空间信息，我们提出了一个两阶段跟踪组件，该组件能够检测在视觉上类似于地面真实目标的候选目标。 （3）为了感知时间信息，我们提出了一种运动模型，该模型能够通过预测位置分布以获得最终的跟踪结果来排除干扰物。

@@

\subsection{跟踪组件}

我们基于流行的对象检测架构来构建跟踪组件 --- faster RCNN \cite{ren2015faster}。尽管本文中并未首次提出使用对象检测模块和基于暹罗的特征提取器进行对象跟踪，但我们的跟踪器相对于相关跟踪算法 \cite{SiamRPN, Wang2018SiamMask, danelljan2019atom, voigtlaender2019siam}具有优势。与SiamRPN \cite{SiamRPN}的输入始终是目标位于中心的图像块相比，我们跟踪组件的输入是整个图像，这意味着目标可能出现在任何空间位置。这防止了网络学习偏向中心位置，从而打破了网络体系结构的空间不变性约束 \cite{SiamRPN++} 。结果，非常深的网络（例如ResNet50 \cite{he2016deep}）可以用作跟踪组件的特征提取器。有关空间不变性限制和中心偏差的详细说明，请参考 \cite{SiamRPN++}。
%because the input of the network is the entire image, instead of the image patch centered on the target, the target will appear in any poisition in the image, so we do not need the network has strict spatial invariance restriction \cite{SiamRPN++}, so we can use a deeper feature extractor, i.e., resnet50. 
与 SiamRPN \cite{SiamRPN} 和 SiamMask \cite{Wang2018SiamMask} 相比，我们使用两阶段体系结构。第二阶段（RoI head \cite{ren2015faster}）可以更有效地区分前景和背景。
与SiamMask \cite{Wang2018SiamMask} 和ATOM \cite{danelljan2019atom}相比，我们的跟踪器可以在整个图像中搜索目标，从而可以在跟踪模块出错后在空间上及时检索目标。
与骨架和RPN被冻结的Siam R-CNN \cite{voigtlaender2019siam}相比，我们的跟踪器在RPN之前会生成目标特定的功能，并且可以端到端地训练整个网络。在对象跟踪中，目标可能是一个视频中的前景而另一个视频中的背景。因此，由我们的RPN生成的候选者可以更好地满足一般对象跟踪的要求。
%(The backbone and RPN are frozen and only the redetection head (after concatenation) is trained for tracking) they fixed the parameters in the backbone and the RPN. Only the second stage is used for target spercific tracking, which is not good for "generatic" object tracking: because some objects are foreground in some cases and background in others. Instead, our tracker use the correlation before RPN, the "target" which is good for general object tracking. The architecture of our tracking component is described as follows:

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
为了描述我们的跟踪组件，我们首先简要回顾一下更快的RCNN。它包括一个特征提取器，其后是两个检测阶段：RPN头和RoI头。
特征提取器 $\phi_{1}$ 是ResNet50的变体。第一阶段使用区域提议网络（RPN）在主干层的最后一个特征图上滑动，并预测是否存在对象，并预测这些对象的边界框。通过执行RoI Align \cite{He2018MaskR} 以从该提议的区域提取深层特征，对RPN建议的每个区域运行第二阶段（即 RoI head）。
使用分类层将每个RoI（感兴趣区域）分类为特定类别，并使用回归层对边界框进行细化。
请参阅 \cite{ren2015faster} 了解更多详细信息。

对于对象跟踪任务，特征提取器 $\phi_{1}$有两个输入：模板图像 $z$ 和搜索图像 $x$。根据暹罗架构的设计，两个输入共享相同的网络参数以提取特征。
在生成模板特征 $f_{z} = \phi_{1}(z)$ 和搜索特征 $f_{x} = \phi_{1}(x)$之后，我们裁剪了对象特征 $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$ 由RoI Align操作 \cite{He2018MaskR} 根据目标的实际情况从模板特征中获取：
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{z}),
\end{equation}
其中 $\mathcal{R}$ 表示RoI Align运算符，而 $b_{obj}$ 是目标的地面真值边界框。
接下来，通过深度互相关 \cite{SiamRPN++} 合并搜索功能和对象功能：
\begin{equation}
    f_{corr} = f_{obj} * f_{x},
\end{equation}
其中 $f_{corr}$ 是融合特征和 $*$ 是深度方向互相关算子。
%The use of RPN (region proposal network) is ...
然后将 $f_{corr}$ 发送到RPN头以生成候选 $B=\{b^{i}_{roi}\}^{i=1:N}$.
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
在第二阶段，对融合特征 $f_{corr}$执行RoI Align操作，为每个RoI生成一个小特征图，其通道尺寸为2048，固定空间范围为 7 $\times$ 7：
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
其中 $b_{roi}^{i}$ 是候选区域 $i$的边界框。
最后，每个RoI被分类为前景/背景。在测试期间，我们选择排名靠前的 $K$ 的RoI作为候选目标，这些目标将在运动模型中进行后处理。

@@

\subsection{运动模型} 使用我们的跟踪组件检测到与给定的第一帧模板对象在视觉上相似的对象区域后，我们使用运动模型消除干扰因素并获得最终的跟踪结果。
通过使用历史轨迹信息和当前帧的外观信息学习目标位置分布，运动模型以端到端的方式工作。
然后，它根据位置分布重新评估候选目标，该位置分布是一个二维热图，用于测量目标位于每个空间位置的可能性。

令 $H_{t}^{k} = \{h_{t-i}\}_{i=1:k}$ 表示历史轨迹信息，其中 $t$ 是当前帧的索引，$k$ 是历史长度，并且 $h_{j} = \{x_{j}, y_{j}\}$ 是一个二维坐标，表示目标在帧 $j$中的位置。
受姿态估计任务的启发，我们将 $h_{j}$ 表示为二维热图 $m_{j} \in \mathbb R^{h \times w}$ ，其中二维高斯定点位于目标位置 $(x_{j}, y_{j})$。
为了对时间信息进行建模，根据时间顺序将生成的 $k$ 热图进行连接，以获得通道张量 $\mathcal{M} \in \mathbb{R}^{k \times h \times w}$ 维度 $k$：
\begin{equation}
    \mathcal{M}_{t}^{k} = \mathcal{C}(m_{t-k}, m_{t-k+1}, ..., m_{t-1}),
\end{equation}
其中 $\mathcal{C}(\cdot)$ 是串联操作。

我们的运动模型不是仅仅利用历史轨迹信息进行预测，但也考虑当前帧的出现信息。
为此，将当前帧 $\mathcal{I} \in \mathbb{R}^{3 \times h \times w}$ 的RGB图像与轨迹张量连接起来，以获得增强的轨迹张量 $\mathcal{N} \in \mathbb{R}^{(3+k) \times h \times w}$ ，通道尺寸为 $(3+k)$：
\begin{equation}
    \mathcal{N}_{t}^{k} = \mathcal{C}(\mathcal{I}_{t}, \mathcal{M}_{t}^{k}).
\end{equation}
假设 $\phi_{2}$ 是运动模型，它是一个CNN网络，则 $\phi_{2}$ 的输出计算如下：
\begin{equation}
    \mathcal{O}_{t}^{k} = \phi_{2}(\mathcal{N}_{t}^{k}),
\end{equation}
其中 $\mathcal{O}_{t}^{k} \in \mathbb{R}^{h \times w}$ 是二维热图，它反映了目标在 $t$帧中的位置分布。

我们的运动模型 $\phi_{2}$ 的网络与姿势估计网络HRNet \cite{sun2019deep}相同。
\iffalse
The main reason why the pose estimation network can be used to design the motion model is that the output of the pose estimation network is the position distribution of joint points, and the output of the motion model is the position distribution of the target. This means that there is a great deal of commonality between the two tasks. In order to use HRNet for trajectory estimation, we need to change the input and output of HRNet and keep the network structure unchanged.

During tracking the $i$-th frame, we utilize the position information of the previous $K$ frames as the input to the network.
Specifically, for a historical frame, a heat map is generated by applying 2D Gaussian with stand deviation of 3 pixels centered on the target position in that frame.
The generated $K$ heatmaps are concatenated according to the time order to obtain the \textbf{trajectory tensor} with channel dimension $K$.
Our motion model not only utilizes the historical trajectory information for prediction, but also considers the appearance information of the current frame.
To achieve this, the RGB image of the current frame and the trajectory tensor are concatenated to obtain the tensor with channel dimension $(3+K)$. This tensor is sent to the network, and the output of the network is a heatmap reflecting the position distribution of the target in the current frame. The loss function, defined as the mean squared error, is applied for comparing the predicted heatmap and the groundtruth heatmap. The groundtruth heatmap is generated by applying 2D Gaussian with standard deviation of 3 pixels centered on the target position in the current frame. The network structure of our motion model is the same as HRNet. 
\fi
这里提供简要说明。 HRNet的第一阶段是高分辨率子网。然后，从高到低分辨率的子网一一添加，以形成更多的阶段。多分辨率子网并联连接。通过在整个过程中一遍又一遍地在并行多分辨率子网中交换信息来进行重复的多尺度融合。我们估计HRNet输出的高分辨率表示上的位置分布。有关网络结构的详细信息，请参考 \cite{sun2019deep}。

\section{实验}
\label{sec:experiments}
\iffalse
\begin{figure}[htb]
    \includegraphics[width=8.6cm]{images/success_plot.png}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.
}
    \label{fig:ao}
\end{figure}
\fi

\subsection{实施细节}
我们的跟踪组件在GOT-10k \cite{GOT-10k} 训练集中进行了训练。它包含超过10000个真实运动对象的视频片段和超过150万个手动标记的边界框，其中包括563类真实运动对象和87类运动模式。
我们执行多尺度训练：目标大小从 $64 \times 64$ to $256 \times 256$不等。图像大小在跟踪过程中保持不变。跟踪组件使用随机梯度下降（SGD）进行训练。我们使用 $10^{-4}$ 的权重衰减和0.9的动量。我们训练跟踪组件进行27k次迭代。学习率从 $10^{-2}$ 降至 $10^{-4}$。

运动模型也通过GOT-10k训练集进行训练。 Adam优化器 \cite{kingma2014adam} 用于培训。基本学习率设置为 $10^{-3}$，并在第170和200个时代分别降至 $10^{-4}$ 和 $10^{-5}$ 。训练过程在210个纪元内终止。
